### 2021-03-13 README.Rmd
new function

This will create a new directory in the working directory, titled "dissertation", that includes a skeleton of a research project to assist the user in getting started on their academic paper/project. The only downside to the console approach over the Rstudio approach is the console approach won't create an `.Rproj` file in the directory. The Rstudio approach will.

>>>>

This will create a new directory in the working directory, titled "dissertation", that includes a skeleton of a research project to assist the user in getting started on their academic paper/project. That directory will be located in the current working directory. The only downside to the console approach over the Rstudio approach is the console approach won't create an `.Rproj` file in the directory. The Rstudio approach will.

You could optionally combine this command line call in the console with the following command, which will add an `.Rproj` file to the directory you just created

```{r, eval=F}
# steveproj::create_project("dissertation")
# ^ assume you just ran this
# Then, do this next
steveproj::create_rproj("dissertation")
```
